---
title: "My Path in Plant Science"
format: html
toc: false
---
My academic journey began at the Bizerte Preparatory Engineering Institute, where my interest in plant biology first started to take shape through the foundational courses I had taken there. This growing curiosity became the main reason I chose to pursue agronomy after the national examination, within the Tunisian Grandes Écoles system, which guides students toward specialized engineering schools based on their ranking and academic orientation. I then joined the Higher Institute of Agronomic Sciences of Chott Mariem, where I specialized in Horticultural Production and developed a stronger connection between plant science, crop management, and applied agronomy. A key step in this journey was my selection for the Erasmus+ exchange program at Agrocampus Ouest Rennes-Angers in France. This experience introduced me to biotechnology-oriented laboratory training and encouraged me to think about plant science from a broader perspective. It also strengthened my interest in multicultural academic environments, where scientific learning is enriched by cultural exchange and collaboration.

My graduation project on Rosa centifolia was motivated by my interest in high-value horticultural species and the role of plant biotechnology in improving propagation and production practices. Working with tissue culture allowed me to explore how laboratory-based techniques can address practical challenges in ornamental and aromatic plant production. Later, my MSc research at the Mediterranean Agronomic Institute of Chania offered a  continuation of this path, linking molecular plant biology with agronomic applications through the study of tomato ripening, fruit quality, and postharvest behaviour.

The following timeline and map highlight the places, institutions, and experiences that have shaped my development as a plant scientist.

```{r}
#| echo: false
#| warning: false
#| message: false

library(htmltools)

timeline_items <- data.frame(
  map_id = c(
    "ipeib",
    "isacm",
    "sanlucar",
    "azib_flower",
    "bioverte",
    "aco",
    "hs_lab",
    "maich",
    "pmbb_lab"
  ),

  time = c(
    "Sep 2017 - Jun 2019",
    "Sep 2019 - Jun 2022",
    "Aug 2020",
    "Jun 2021",
    "Jul 2021",
    "Sep 2021 - Feb 2022",
    "Jun 2022 - Dec 2022",
    "Sep 2024 - Present",
    "Oct 2025 - Present"
  ),

  title = c(
    "Bizerte Preparatory Engineering Institute",
    "Higher Institute of Agronomic Sciences of Chott Mariem",
    "Sanlucar",
    "Azib Flower",
    "Bioverte",
    "Agrocampus Ouest Rennes-Angers",
    "Horticultural Sciences Laboratory, INAT",
    "Mediterranean Agronomic Institute of Chania",
    "Plant Molecular Biology and Biotechnology Laboratory, MAICh"
  ),

  short_title = c(
    "IPEIB",
    "ISACM",
    "Sanlucar",
    "Azib Flower",
    "Bioverte",
    "ACO",
    "HS Lab",
    "MAICh",
    "PMBB Lab"
  ),

  role = c(
    "Pre-Engineering courses in Biology-Geology",
    "Agronomy Engineering - Horticultural Production",
    "Internship",
    "Internship",
    "Internship",
    "Erasmus Exchange Program",
    "Graduation Thesis",
    "Master of Science - Horticultural Genetics and Biotechnology",
    "Graduation Thesis"
  ),

  description = c(
    "Built a foundation in plant & animal biology, geology, and chemistry.",
    "Specialized in horticultural production.",
    "Worked on hydroponic systems for red berries production.",
    "Worked on ornamental greenhouse operations and practiced integrated pest management.",
    "Explored sustainable beekeeping, hive management, and honey extraction.",
    "Completed an international exchange program focused on agronomy and horticultural sciences.",
    "Optimization of Tissue Culture Protocol for Rosa centifolia.",
    "Advanced training in horticultural genetics, biotechnology, plant physiology, and molecular biology.",
    "Functional Characterization of 7 Local Greek Tomato Cultivars in Ripening."
  ),

  category = c(
    "Education",
    "Education",
    "Industry",
    "Industry",
    "Industry",
    "Education",
    "Research",
    "Education",
    "Research"
  ),

  stringsAsFactors = FALSE
)

timeline_items$position <- ifelse(
  timeline_items$category == "Education",
  "top",
  "bottom"
)

timeline_items$color <- ifelse(
  timeline_items$category == "Education", "#66c5cc",
  ifelse(timeline_items$category == "Research", "#f89c74", "#f6cf71")
)

timeline_html <- tagList(
  tags$style(HTML("
    .aj3-timeline-wrapper {
      width: 100%;
      margin: 18px 0 35px 0;
      overflow: visible;
    }

    .aj3-timeline {
      position: relative;
      display: grid;
      grid-template-columns: repeat(9, minmax(0, 1fr));
      grid-template-rows: 62px 34px 62px;
      column-gap: 4px;
      width: 100%;
      overflow: visible;
    }

    .aj3-timeline::before {
      content: '';
      position: absolute;
      left: 0;
      right: 0;
      top: 50%;
      height: 3px;
      background: #d5d5d5;
      transform: translateY(-50%);
      z-index: 0;
    }

    .aj3-item {
      position: relative;
      display: grid;
      grid-template-rows: 62px 34px 62px;
      z-index: 1;
      min-width: 0;
    }

    .aj3-top,
    .aj3-bottom {
      display: flex;
      justify-content: center;
      text-align: center;
      min-width: 0;
    }

    .aj3-top {
      align-items: flex-end;
      padding-bottom: 6px;
    }

    .aj3-bottom {
      align-items: flex-start;
      padding-top: 6px;
    }

    .aj3-axis {
      position: relative;
    }

    .aj3-node {
      position: absolute;
      left: 50%;
      top: 50%;
      width: 15px;
      height: 15px;
      border-radius: 50%;
      border: 2px solid white;
      box-shadow: 0 0 0 1px #bdbdbd;
      transform: translate(-50%, -50%);
      z-index: 3;
    }

    .aj3-connector-top {
      position: absolute;
      left: 50%;
      top: 0;
      bottom: 50%;
      width: 2px;
      background: #d0d0d0;
      transform: translateX(-50%);
      z-index: 2;
    }

    .aj3-connector-bottom {
      position: absolute;
      left: 50%;
      top: 50%;
      bottom: 0;
      width: 2px;
      background: #d0d0d0;
      transform: translateX(-50%);
      z-index: 2;
    }

    .aj3-name {
      cursor: pointer;
      font-family: inherit;
      font-weight: 700;
      font-size: 0.78rem;
      line-height: 1.15;
      color: #2c3e50;
      background: white;
      border: 1px solid #e2e2e2;
      border-radius: 8px;
      padding: 5px 8px;
      box-shadow: 0 1px 3px rgba(0,0,0,0.06);
      max-width: 105px;
      transition: background 0.15s ease, box-shadow 0.15s ease;
    }

    .aj3-name:hover {
      background: #f7f7f7;
      box-shadow: 0 2px 6px rgba(0,0,0,0.10);
    }

    .aj3-name.aj3-active {
      background: #f1f1f1;
      box-shadow: 0 2px 7px rgba(0,0,0,0.13);
    }

    .aj3-floating-popup {
      display: none;
      position: fixed;
      width: 300px;
      background: white;
      border: 1px solid #dddddd;
      border-radius: 12px;
      padding: 13px 14px 14px 14px;
      box-shadow: 0 5px 18px rgba(0,0,0,0.22);
      text-align: left;
      z-index: 999999;
    }

    .aj3-popup-close {
      position: absolute;
      top: 8px;
      right: 9px;
      border: none;
      background: transparent;
      font-size: 1rem;
      line-height: 1;
      cursor: pointer;
      color: #777777;
      padding: 2px 4px;
    }

    .aj3-popup-close:hover {
      color: #222222;
    }

    .aj3-popup-meta {
      display: flex;
      align-items: center;
      justify-content: space-between;
      gap: 8px;
      margin-bottom: 9px;
      padding-right: 20px;
    }

    .aj3-popup-category {
      display: inline-flex;
      align-items: center;
      gap: 6px;
      font-size: 0.73rem;
      color: #555555;
      background: #f4f4f4;
      padding: 3px 8px;
      border-radius: 999px;
      white-space: nowrap;
    }

    .aj3-popup-dot {
      display: inline-block;
      width: 9px;
      height: 9px;
      border-radius: 50%;
      flex: 0 0 auto;
    }

    .aj3-popup-time {
      font-weight: 700;
      font-size: 0.78rem;
      color: #444444;
      white-space: nowrap;
    }

    .aj3-popup-title {
      font-weight: 700;
      font-size: 1rem;
      color: #2c3e50;
      line-height: 1.25;
      margin-bottom: 8px;
    }

    .aj3-popup-role {
      font-size: 0.84rem;
      color: #4f4f4f;
      line-height: 1.35;
      margin-bottom: 8px;
      font-weight: 600;
    }

    .aj3-popup-description {
      font-size: 0.81rem;
      color: #666666;
      line-height: 1.38;
    }

    @media (max-width: 900px) {
      .aj3-name {
        font-size: 0.68rem;
        max-width: 82px;
        padding: 4px 5px;
      }

      .aj3-floating-popup {
        width: 245px;
      }

      .aj3-popup-meta {
        align-items: flex-start;
        flex-direction: column;
        gap: 5px;
      }

      .aj3-popup-time {
        white-space: normal;
      }
    }
  ")),

  tags$div(
    class = "aj3-timeline-wrapper",

    tags$div(
      class = "aj3-timeline",

      lapply(seq_len(nrow(timeline_items)), function(i) {
        is_top <- timeline_items$position[i] == "top"

        name_button <- tags$button(
          type = "button",
          class = "aj3-name",
          `data-map-id` = timeline_items$map_id[i],
          `data-title` = timeline_items$title[i],
          `data-time` = timeline_items$time[i],
          `data-role` = timeline_items$role[i],
          `data-description` = timeline_items$description[i],
          `data-category` = timeline_items$category[i],
          `data-color` = timeline_items$color[i],
          `data-position` = timeline_items$position[i],
          timeline_items$short_title[i]
        )

        tags$div(
          class = "aj3-item",

          if (is_top) {
            tags$div(class = "aj3-top", name_button)
          } else {
            tags$div(class = "aj3-top")
          },

          tags$div(
            class = "aj3-axis",
            tags$div(
              class = if (is_top) "aj3-connector-top" else "aj3-connector-bottom"
            ),
            tags$div(
              class = "aj3-node",
              style = paste0("background:", timeline_items$color[i], ";")
            )
          ),

          if (!is_top) {
            tags$div(class = "aj3-bottom", name_button)
          } else {
            tags$div(class = "aj3-bottom")
          }
        )
      })
    ),

    tags$div(class = "aj3-floating-popup")
  ),

  tags$script(HTML("
    (function() {
      function escapeHtml(value) {
        return String(value)
          .replace(/&/g, '&amp;')
          .replace(/</g, '&lt;')
          .replace(/>/g, '&gt;')
          .replace(/\"/g, '&quot;')
          .replace(/'/g, '&#039;');
      }

      function initAcademicJourneyTimeline() {
        var wrapper = document.querySelector('.aj3-timeline-wrapper');

        if (!wrapper || wrapper.dataset.initialized === 'true') {
          return;
        }

        wrapper.dataset.initialized = 'true';

        var popup = wrapper.querySelector('.aj3-floating-popup');
        var activeButton = null;

        function closePopup() {
          popup.style.display = 'none';
          popup.innerHTML = '';

          wrapper.querySelectorAll('.aj3-name').forEach(function(button) {
            button.classList.remove('aj3-active');
          });

          activeButton = null;
        }

        function positionPopup(button) {
          var rect = button.getBoundingClientRect();
          var margin = 12;

          popup.style.display = 'block';

          var popupWidth = popup.offsetWidth;
          var popupHeight = popup.offsetHeight;

          var below = rect.bottom + margin;
          var above = rect.top - popupHeight - margin;

          var preferredTop;

          if (button.getAttribute('data-position') === 'top') {
            preferredTop = below;
          } else {
            preferredTop = above;
          }

          if (preferredTop < margin) {
            preferredTop = below;
          }

          if (preferredTop + popupHeight > window.innerHeight - margin) {
            preferredTop = above;
          }

          var top = Math.max(
            margin,
            Math.min(preferredTop, window.innerHeight - popupHeight - margin)
          );

          var left = rect.left + rect.width / 2 - popupWidth / 2;

          left = Math.max(
            margin,
            Math.min(left, window.innerWidth - popupWidth - margin)
          );

          popup.style.top = top + 'px';
          popup.style.left = left + 'px';
        }

        function openPopup(button) {
          var title = button.getAttribute('data-title');
          var time = button.getAttribute('data-time');
          var role = button.getAttribute('data-role');
          var description = button.getAttribute('data-description');
          var category = button.getAttribute('data-category');
          var color = button.getAttribute('data-color');

          popup.innerHTML =
            '<button type=\"button\" class=\"aj3-popup-close\" aria-label=\"Close\">×</button>' +
            '<div class=\"aj3-popup-meta\">' +
              '<div class=\"aj3-popup-category\">' +
                '<span class=\"aj3-popup-dot\" style=\"background:' + escapeHtml(color) + ';\"></span>' +
                escapeHtml(category) +
              '</div>' +
              '<div class=\"aj3-popup-time\">' + escapeHtml(time) + '</div>' +
            '</div>' +
            '<div class=\"aj3-popup-title\">' + escapeHtml(title) + '</div>' +
            '<div class=\"aj3-popup-role\">' + escapeHtml(role) + '</div>' +
            '<div class=\"aj3-popup-description\">' + escapeHtml(description) + '</div>';

          wrapper.querySelectorAll('.aj3-name').forEach(function(item) {
            item.classList.remove('aj3-active');
          });

          button.classList.add('aj3-active');
          activeButton = button;

          positionPopup(button);

          var closeButton = popup.querySelector('.aj3-popup-close');

          if (closeButton) {
            closeButton.addEventListener('click', function(event) {
              event.stopPropagation();
              closePopup();
            });
          }
        }

        wrapper.querySelectorAll('.aj3-name').forEach(function(button) {
          button.addEventListener('click', function(event) {
            event.stopPropagation();

            if (activeButton === button && popup.style.display === 'block') {
              closePopup();
            } else {
              openPopup(button);

              window.dispatchEvent(
                new CustomEvent('academicJourneySelect', {
                  detail: {
                    mapId: button.getAttribute('data-map-id')
                  }
                })
              );
            }
          });
        });

        popup.addEventListener('click', function(event) {
          event.stopPropagation();
        });

        document.addEventListener('click', function() {
          closePopup();
        });

        window.addEventListener('resize', function() {
          if (activeButton && popup.style.display === 'block') {
            positionPopup(activeButton);
          }
        });

        window.addEventListener('scroll', function() {
          if (activeButton && popup.style.display === 'block') {
            positionPopup(activeButton);
          }
        });
      }

      if (document.readyState === 'loading') {
        document.addEventListener('DOMContentLoaded', initAcademicJourneyTimeline);
      } else {
        initAcademicJourneyTimeline();
      }
    })();
  "))
)

timeline_html
```

```{r}
#| echo: false
#| warning: false
#| message: false
#| toc: false
#| fig-width: 10
#| fig-height: 6

library(leaflet)
library(sf)
library(rnaturalearth)
library(htmlwidgets)
library(htmltools)

places <- data.frame(
  map_id = c(
    # Education
    "maich",
    "aco",
    "isacm",
    "ipeib",

    # Research
    "pmbb_lab",
    "hs_lab",

    # Industry
    "azib_flower",
    "bioverte",
    "sanlucar"
  ),

  name = c(
    # Education
    "Mediterranean Agronomic Institute of Chania",
    "Agrocampus Ouest Rennes-Angers",
    "Higher Institute of Agronomic Sciences of Chott Mariem",
    "Bizerte Preparatory Engineering Institute",

    # Research
    "Plant Molecular Biology and Biotechnology Laboratory, MAICh",
    "Horticultural Science Laboratory, National Agronomic Institute of Tunisia",

    # Industry
    "Azib Flower",
    "Bioverte",
    "Sanlucar"
  ),

  category = c(
    "Education", "Education", "Education", "Education",
    "Research", "Research",
    "Industry", "Industry", "Industry"
  ),

  location = c(
    "Chania, Greece",
    "Angers, France",
    "Sousse / Chott Mariem, Tunisia",
    "Bizerte, Tunisia",
    "Chania, Greece",
    "Tunis, Tunisia",
    "Bizerte, Tunisia",
    "Bizerte, Tunisia",
    "Bizerte, Tunisia"
  ),

  country = c(
    "Greece", "France", "Tunisia", "Tunisia",
    "Greece", "Tunisia", "Tunisia", "Tunisia", "Tunisia"
  ),

  place_group = c(
    "Chania",
    "Angers",
    "Sousse / Chott Mariem",
    "Bizerte",
    "Chania",
    "Tunis",
    "Bizerte",
    "Bizerte",
    "Bizerte"
  ),

  base_lat = c(
    35.5138,
    47.4784,
    35.9230,
    37.2744,
    35.5138,
    36.8189,
    37.2744,
    37.2744,
    37.2744
  ),

  base_lng = c(
    24.0180,
    -0.5632,
    10.5600,
    9.8739,
    24.0180,
    10.1658,
    9.8739,
    9.8739,
    9.8739
  ),

  stringsAsFactors = FALSE
)

# Category colors
col_education <- "#66c5cc"
col_research  <- "#f89c74"
col_industry  <- "#f6cf71"

places$marker_color <- ifelse(
  places$category == "Education", col_education,
  ifelse(places$category == "Research", col_research, col_industry)
)

places$marker_radius <- ifelse(
  places$category == "Education", 5.5,
  ifelse(places$category == "Research", 5.0, 4.5)
)

places$marker_weight <- ifelse(
  places$category == "Education", 2.2,
  ifelse(places$category == "Research", 2.0, 1.8)
)

places$marker_opacity <- ifelse(
  places$category == "Education", 0.96,
  ifelse(places$category == "Research", 0.88, 0.84)
)

# Minimal map popup: name + location only
places$popup <- paste0(
  "<div class='aj-map-popup-title'>", places$name, "</div>",
  "<div class='aj-map-popup-location'>", places$location, "</div>"
)

# ---------------------------------------------------------
# Radial display coordinates for overlapping places
# ---------------------------------------------------------

places$lat <- places$base_lat
places$lng <- places$base_lng

offset_distance <- 0.11

for (grp in unique(places$place_group)) {
  idx <- which(places$place_group == grp)
  n <- length(idx)

  if (n > 1) {
    angles <- seq(0, 2 * pi, length.out = n + 1)[-1]

    if (grp == "Chania") {
      angles <- angles + pi / 4
    }

    if (grp == "Bizerte") {
      angles <- angles + pi / 6
    }

    places$lat[idx] <- places$base_lat[idx] + offset_distance * sin(angles)
    places$lng[idx] <- places$base_lng[idx] + offset_distance * cos(angles)
  }
}

# ---------------------------------------------------------
# Pin overlap priority:
# Research on top, then Education, then Industry.
# ---------------------------------------------------------

places$priority <- ifelse(
  places$category == "Industry", 1,
  ifelse(places$category == "Education", 2, 3)
)

places <- places[order(places$priority), ]

world <- ne_countries(scale = "medium", returnclass = "sf")
study_countries <- world[world$admin %in% unique(places$country), ]

# ---------------------------------------------------------
# Map styling to match timeline section
# ---------------------------------------------------------

map_style <- tags$style(HTML("
  .aj-map-category-filter {
    background: white;
    padding: 10px 12px;
    border: 1px solid #dddddd;
    border-radius: 12px;
    box-shadow: 0 5px 18px rgba(0,0,0,0.18);
    line-height: 1.4;
    font-size: 13px;
    min-width: 140px;
    color: #2c3e50;
  }

  .aj-map-category-title {
    font-weight: 700;
    margin-bottom: 7px;
    color: #2c3e50;
  }

  .aj-map-category-item {
    cursor: pointer;
    display: flex;
    align-items: center;
    gap: 7px;
    margin-bottom: 5px;
    padding: 4px 6px;
    border-radius: 8px;
    color: #555555;
    transition: background 0.15s ease, opacity 0.15s ease;
  }

  .aj-map-category-item:last-child {
    margin-bottom: 0;
  }

  .aj-map-category-item:hover {
    background: #f7f7f7;
  }

  .aj-map-category-item.aj-map-active {
    background: #f1f1f1;
    font-weight: 700;
    color: #2c3e50;
    opacity: 1;
  }

  .aj-map-category-item.aj-map-faded {
    opacity: 0.55;
  }

  .aj-map-category-dot {
    display: inline-block;
    width: 11px;
    height: 11px;
    border-radius: 50%;
    flex: 0 0 auto;
  }

  .aj-map-popup .leaflet-popup-content-wrapper {
    border-radius: 12px;
    border: 1px solid #dddddd;
    box-shadow: 0 5px 18px rgba(0,0,0,0.22);
  }

  .aj-map-popup .leaflet-popup-content {
    margin: 12px 14px;
    font-family: inherit;
  }

  .aj-map-popup .leaflet-popup-tip {
    background: white;
  }

  .aj-map-popup-title {
    font-weight: 700;
    font-size: 0.95rem;
    color: #2c3e50;
    line-height: 1.25;
    margin-bottom: 5px;
  }

  .aj-map-popup-location {
    font-size: 0.82rem;
    color: #666666;
    line-height: 1.35;
  }

  .leaflet-control-zoom a {
    color: #2c3e50 !important;
  }
"))

category_filter <- HTML(paste0(
  "
  <div class='aj-map-category-filter'>

    <div class='aj-map-category-title'>Categories</div>

    <div class='aj-map-category-item' data-group='Education'>
      <span class='aj-map-category-dot' style='background:", col_education, ";'></span>
      <span>Education</span>
    </div>

    <div class='aj-map-category-item' data-group='Research'>
      <span class='aj-map-category-dot' style='background:", col_research, ";'></span>
      <span>Research</span>
    </div>

    <div class='aj-map-category-item' data-group='Industry'>
      <span class='aj-map-category-dot' style='background:", col_industry, ";'></span>
      <span>Industry</span>
    </div>

  </div>
  "
))

map_widget <- leaflet(
  options = leafletOptions(
    zoomControl = TRUE,
    attributionControl = FALSE
  )
) |>

  addMapPane("industryPane", zIndex = 420) |>
  addMapPane("educationPane", zIndex = 430) |>
  addMapPane("researchPane", zIndex = 440) |>

  addPolygons(
    data = world,
    color = "#b8b8b8",
    weight = 0.6,
    fillColor = "white",
    fillOpacity = 1,
    opacity = 1
  ) |>

  addPolygons(
    data = study_countries,
    layerId = ~paste0("study-", admin),
    color = "#777777",
    weight = 1.1,
    fillColor = "#d9d9d9",
    fillOpacity = 0.10,
    opacity = 1,
    highlightOptions = highlightOptions(
      weight = 2.2,
      color = "#555555",
      fillColor = "#c7c7c7",
      fillOpacity = 0.35,
      bringToFront = FALSE
    )
  ) |>

  addCircleMarkers(
    data = subset(places, category == "Industry"),
    lng = ~lng,
    lat = ~lat,
    layerId = ~map_id,
    radius = ~marker_radius,
    color = col_industry,
    weight = ~marker_weight,
    fillColor = col_industry,
    fillOpacity = ~marker_opacity,
    opacity = 1,
    popup = ~popup,
    popupOptions = popupOptions(className = "aj-map-popup"),
    group = "Industry",
    options = pathOptions(
      pane = "industryPane",
      bubblingMouseEvents = FALSE
    )
  ) |>

  addCircleMarkers(
    data = subset(places, category == "Education"),
    lng = ~lng,
    lat = ~lat,
    layerId = ~map_id,
    radius = ~marker_radius,
    color = col_education,
    weight = ~marker_weight,
    fillColor = col_education,
    fillOpacity = ~marker_opacity,
    opacity = 1,
    popup = ~popup,
    popupOptions = popupOptions(className = "aj-map-popup"),
    group = "Education",
    options = pathOptions(
      pane = "educationPane",
      bubblingMouseEvents = FALSE
    )
  ) |>

  addCircleMarkers(
    data = subset(places, category == "Research"),
    lng = ~lng,
    lat = ~lat,
    layerId = ~map_id,
    radius = ~marker_radius,
    color = col_research,
    weight = ~marker_weight,
    fillColor = col_research,
    fillOpacity = ~marker_opacity,
    opacity = 1,
    popup = ~popup,
    popupOptions = popupOptions(className = "aj-map-popup"),
    group = "Research",
    options = pathOptions(
      pane = "researchPane",
      bubblingMouseEvents = FALSE
    )
  ) |>

  addControl(
    html = category_filter,
    position = "bottomright",
    className = "aj-map-category-control"
  ) |>

  fitBounds(
    lng1 = min(places$lng) - 8,
    lat1 = min(places$lat) - 4,
    lng2 = max(places$lng) + 8,
    lat2 = max(places$lat) + 4
  ) |>

  onRender(
    "
    function(el, x) {
      var map = this;
      var studyLayers = [];
      var markersById = {};
      var allMarkers = [];

      function resetStudyCountries() {
        studyLayers.forEach(function(layer) {
          layer.setStyle({
            color: '#777777',
            weight: 1.1,
            fillColor: '#d9d9d9',
            fillOpacity: 0.10,
            opacity: 1
          });
        });
      }

      map.eachLayer(function(layer) {
        if (
          layer.options &&
          layer.options.layerId &&
          layer.options.layerId.startsWith('study-')
        ) {
          studyLayers.push(layer);

          layer.on('click', function() {
            resetStudyCountries();

            layer.setStyle({
              color: '#555555',
              weight: 2.4,
              fillColor: '#c7c7c7',
              fillOpacity: 0.42,
              opacity: 1
            });
          });
        }

        if (
          layer.options &&
          layer.options.layerId &&
          layer instanceof L.CircleMarker
        ) {
          markersById[layer.options.layerId] = layer;
          allMarkers.push(layer);
        }
      });

      var panes = {
        Education: map.getPane('educationPane'),
        Research: map.getPane('researchPane'),
        Industry: map.getPane('industryPane')
      };

      function showAllCategories() {
        Object.keys(panes).forEach(function(groupName) {
          panes[groupName].style.display = '';
        });

        map.closePopup();

        var items = el.querySelectorAll('.aj-map-category-item');

        items.forEach(function(item) {
          item.classList.remove('aj-map-active');
          item.classList.remove('aj-map-faded');
        });
      }

      function showOnlyCategory(selectedGroup) {
        Object.keys(panes).forEach(function(groupName) {
          if (groupName === selectedGroup) {
            panes[groupName].style.display = '';
          } else {
            panes[groupName].style.display = 'none';
          }
        });

        map.closePopup();

        var items = el.querySelectorAll('.aj-map-category-item');

        items.forEach(function(item) {
          var itemGroup = item.getAttribute('data-group');

          if (itemGroup === selectedGroup) {
            item.classList.add('aj-map-active');
            item.classList.remove('aj-map-faded');
          } else {
            item.classList.remove('aj-map-active');
            item.classList.add('aj-map-faded');
          }
        });
      }

      function resetMarkerStyles() {
        allMarkers.forEach(function(marker) {
          if (marker.options && marker.options.originalRadius) {
            marker.setRadius(marker.options.originalRadius);
          }

          marker.setStyle({
            weight: marker.options.originalWeight || marker.options.weight,
            opacity: 1
          });
        });
      }

      allMarkers.forEach(function(marker) {
        marker.options.originalRadius = marker.options.radius;
        marker.options.originalWeight = marker.options.weight;
      });

      function focusMapPoint(mapId) {
        var marker = markersById[mapId];

        if (!marker) {
          return;
        }

        showAllCategories();
        resetMarkerStyles();

        marker.setRadius((marker.options.originalRadius || marker.options.radius) + 2.5);
        marker.setStyle({
          weight: (marker.options.originalWeight || marker.options.weight) + 1,
          opacity: 1
        });

        var latlng = marker.getLatLng();

        map.flyTo(latlng, Math.max(map.getZoom(), 5), {
          animate: true,
          duration: 0.6
        });

        setTimeout(function() {
          marker.openPopup();
        }, 650);

        setTimeout(function() {
          resetMarkerStyles();
        }, 2200);

        el.scrollIntoView({
          behavior: 'smooth',
          block: 'center'
        });
      }

      var categoryFilter = el.querySelector('.aj-map-category-filter');

      if (categoryFilter) {
        L.DomEvent.disableClickPropagation(categoryFilter);
        L.DomEvent.disableScrollPropagation(categoryFilter);

        var items = categoryFilter.querySelectorAll('.aj-map-category-item');

        items.forEach(function(item) {
          item.addEventListener('click', function(event) {
            event.stopPropagation();

            var selectedGroup = item.getAttribute('data-group');
            showOnlyCategory(selectedGroup);
          });
        });
      }

      map.on('click', function() {
        showAllCategories();
      });

      window.addEventListener('academicJourneySelect', function(event) {
        if (event.detail && event.detail.mapId) {
          focusMapPoint(event.detail.mapId);
        }
      });

      showAllCategories();
    }
    "
  )

tagList(
  map_style,
  map_widget
)
```
